### 2015-10-07 postdoctoral/S_prime_kappa.tex
add nearly complete omega_2 proof

  \begin{remark}
    Scheeper's \(S(\kappa)\) requiring injections is stronger than my
    \(S'(\kappa)\) requiring finite-to-one maps. Dow suggests that
    \(S'(\omega_2)\) holds in ZFC. Here's my writeup of his argument.
  \end{remark}

@@

  \begin{claim*}
    There exists a topology on \(\omega_2\) which is locally countable
    and \(\aleph_0\)-bounded.
  \end{claim*}

  \begin{proposition}
    A space which is locally countable and \(\omega\)-bounded is also
    locally compact, locally second-countable, and scattered.
  \end{proposition}

  \begin{proof}
    A countable neighborhood has compact closure by \(\omega\)-boundedness,
    which gives local compactness.

    By local countability, we have local secound-countability.

    TODO: figure out trick to get scattered.
  \end{proof}

  \begin{theorem*}
    \(S'(\omega_2)\).
  \end{theorem*}

  \begin{proof}
    For \(\alpha<\omega_2\), let \(W_\alpha\) be the
    intersection of a countable and compact neighborhood in the claimed topology
    on \(\omega_2\).
  \end{proof}

>>>>

  \begin{remark}
    Scheeper's \(S(\kappa)\) requiring injections is stronger than my
    \(S'(\kappa)\) requiring finite-to-one maps. Dow suggests that
    \(S'(\omega_\omega)\) holds in ZFC by the following.
  \end{remark}

@@

  \begin{theorem}
    There exists a topology on \(\omega_2\) which
    is \(\omega\)-bounded, locally compact, and locally countable.
  \end{theorem}

  \begin{proof}
    Note that the natural linear order on \(\omega_1\) induces such
    a topology for it.

    Let \(\alpha<\omega_2\), and suppose we've defined compatible topologies on
    \(\omega_1\cdot (\beta+1)\) for all \(0\leq\beta<\alpha\).
    If \(\alpha=\beta+1\), then let
    \(\omega_1\cdot(\alpha+1)=\omega_1\cdot(\beta+2)\) be the topological sum
    of the previously defined \(\omega_1\cdot(\beta+1)\) and the linear order
    on \(\omega_1\cdot(\beta+2)\setminus\omega_1\cdot(\beta+1)\cong\omega_1\).
    Similarly, if \(cf(\alpha)>\omega\), then let \(\omega_1\cdot(\alpha+1)\)
    be the topological sum of \(\bigcup_{\beta<\alpha}\omega_1\cdot(\beta+1)\)
    and the linear order on
    \(\omega_1\cdot(\alpha+1)\setminus\omega_1\cdot\alpha\cong\omega_1\).

    The remaining case is where \(\alpha\) is the limit of increasing
    \(\alpha_n\) for \(n<\omega\). Fix a bijection
    \(
      f_\alpha
        :
      \omega_1\cdot(\alpha+1)\setminus\omega_1\cdot\alpha
        \to
      \omega_1\cdot\alpha
    \). Points in \(\omega_1\cdot(\alpha_n+1)\) for some \(n<\omega\)
    have their usual base induced by that previously defined topology. So let
    \(\gamma\in\omega_1\cdot(\alpha+1)\setminus\omega_1\cdot\alpha\).
    Basic open neighborhoods of \(\gamma\) are of the form
    \(
      [\gamma',\gamma]
        \cup
      f_\alpha[[\omega_1\cdot\alpha,\gamma]]
        \setminus
      \omega_1\cdot(\alpha_n+1)
    \),
    where \(\omega_1\cdot\alpha\leq\gamma'<\gamma\)
    and \(n<\omega\).

    We wish to show that \(\omega_2\) with the topology induced by
    \(\bigcup_{\alpha<\omega_2}\omega_1\cdot(\alpha+1)\) is \(\omega\)-bounded,
    locally compact, and locally countable. If
    \(\gamma\in\omega_1\cdot(\alpha+1)\setminus\omega_1\cdot\alpha\) where
    \(cf(\alpha)\not=\omega\), then we immediately see that it is in a clopen
    copy of \(\omega_1\) giving us local compactness and local countability
    immediately. Otherwise, \(\gamma\) has a basic open neighborhood of the form
    \(
      [\gamma',\gamma]
        \cup
      f_\alpha[[\omega_1\cdot\alpha,\gamma]]
        \setminus
      \omega_1\cdot(\alpha_n+1)
    \),
    which is obviously countable. Likewise, its closure is compact:
    the closure operation does not add any ordinals greater than \(\gamma\),
    and any open cover
    contains another basic open neighborhood of \(\gamma\) such as
    \(
      [\gamma'',\gamma]
        \cup
      f_\alpha[[\omega_1\cdot\alpha,\gamma]]
        \setminus
      \omega_1\cdot(\alpha_m+1)
    \)
    which misses only the compact set \([\gamma',\gamma'']\) and the
    closure of the countable set
    \(
      f_\alpha[[\omega_1\cdot\alpha,\gamma]]
        \cap
      \omega_1\cdot(\alpha_{\min(m,n)}+1)
    \), which will be proven to be compact once we show that
    \(\omega_1\cdot(\alpha+1)\) is \(\omega\)-bounded for all
    \(\alpha<\omega_2\). This also will show that \(\omega_2\) with our
    topology is itself \(\omega\)-compact, finishing the proof.

  \end{proof}

  \begin{theorem*}
    \(S'(\omega_\omega)\).
  \end{theorem*}
